Verifying Demonstrations

### 2018-11-27 paper/protocol.tex
Introduces \corr for the proof of correctness of \pid, \wid

\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.
The protester computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the protester uploads the tuple \[  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})\] for permanent storage.

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is to make the time interval as early as possible, whoever is the faster 
will submit it.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid}\) as follows:
\begin{multline*}
  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[ \psh_W = (\cid, \pid, \wid, t_s, 
  t_s', t_e', l, \pi_{\wid}) \] for permanent storage.

@@

To verify the participation count for a subprotest \(\sprtst = (\cid, t, l)\) 
(see \cref{DefProtest}), a verifier must download all the proof shares \[
  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
  t_e^{\prime   (i)}, l_i, \prf_{\pid_j}^{(i)}, \prf_{\wid_i})
\] for each protester \(j\) from the ledger, verify \(\prf_{\pid_j}^{(i)}\), 
\(\prf_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, t_s^{\prime 
      (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
\(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.

>>>>

\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.

The protester computes \iac{NIZK} proof \(\corr_{\pid}\), which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \corr_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the protester uploads the tuple \[
  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \corr_{\pid})
\] for permanent storage.

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is to make the time interval as early as possible, whoever is the faster 
will submit it.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage.

@@

To verify the participation count for a subprotest \(\sprtst = (\cid, t, l)\) 
(see \cref{DefProtest}), a verifier must download all the proof shares \[
  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
\(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.
